Week 5  - Chapter 7 pt. 2 - Analysis

### 2024-11-07 draftdata.Rmd
checkinwithjochempush
unnecessarypushbutheyherewego

>>>>

Information about data set:

-   Data set provided by Jochem

-   collaborations of scholars in NL

-   time frame: ?

    -   timeframe of focus

## DV: Collaboration between scholars

## Covariate 1: Gender

-   assumed binary for simplicity and ethical considerations of assuming gender based on other characterstics

-   Names of scholars manually checked in Dutch Voornamenbank website **(NAME WEBSITE)**

-   with 0 = female and 1 = male.

-

## Covariate 2: Prestige

-   indicated by H-Index: and i10 index

-   definitions indeces:

-

-   number of citations and publications webscraped through OpenAlex **[source]**

-   h index and i10 index calculated based on these counts

```{=html}
<!-- -->
```
-

### 2024-11-07 revisitwithJochem.Rmd
unnecessarypushbutheyherewego

```{r combine gender set}
df <- test$data
df_ego <- do.call(rbind.data.frame, df$demographics)

soc_gender <- soc_gender[,c("Naam", "gender")]
pol_gender <- pol_gender[,c("Naam", "gender")]

gender <- rbind(soc_gender, pol_gender) # combining data sets

df_ego <- df_ego %>% 
            left_join(gender) #dataset 
```

@@

plot(test_w1,
vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), #now, I can use actor attributes for plotting.
vertex.label = NA,
edge.width = 0.2,
edge.arrow.size =0.2)

>>>>

```{r combine gender set}
df <- test$data # make dataset with all data 
df_ego <- do.call(rbind.data.frame, df$demographics) # dataset with demographic information

soc_gender <- soc_gender[,c("Naam", "gender")] # selecting only the content we need
pol_gender <- pol_gender[,c("Naam", "gender")] # selecting only the content we need

gender <- rbind(soc_gender, pol_gender) # combining the gender data sets

df_ego <- df_ego %>% 
            left_join(gender) #dcombininf dataset of gender with the one with demographic information 
```

@@

plot(test_w1,
vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), #now, I can use actor attributes for plotting.
# here: if gender = 1 (aka man) then red dot, if not then blue 
vertex.label = NA,
edge.width = 0.2,
edge.arrow.size =0.2)

### 2024-11-07 week5-2.Rmd
unnecessarypushbutheyherewego

```
THIS IS ALL THE EFFECTS YOU COULD LOOK AT IN YOUR NETWORK 
e.g. outdegree (density), called density, three things: evaluation, endowment, and creation
  you can only include two of the three (tie creation, breaking and maintaining)
  Assumption mechanisms to make and breaka a tie are the same so we only use the EVALUATION part

  All these effects are described in the manual of RSiena Chapter 12 (9?)

@@

```
inpope ppl with lots of indegrees will havelotof indegrees later (in population)
 outAct ppl with lots of outdegrees will have lot of indegrees later

 hint for my own project: interaction effect of these statistics and the effect of gender

>>>>

```
THIS IS ALL THE EFFECTS YOU COULD LOOK AT IN YOUR NETWORK 
e.g. outdegree (density), called density, three things: evaluation, endowment, and creation
  you can only include two of the three (tie creation, breaking and maintaining)

The assumption is: mechanisms to make and break a a tie are the same so WE ONLY USE THE EVALUATION part

  All these effects are described in the manual of RSiena Chapter 12!

@@

```
over time:
inpope ppl with lots of indegrees will havelot of indegrees later (in population)
 outAct ppl with lots of outdegrees will have lot of indegrees later

 hint FOR MY OWN PROJECT: interaction effect of these statistics and the effect of gender
